Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-05 workflow/workflow.Rmd
inf norm values resp

[DR: Fanny, did you figure out why we get infinite values? If not, we need to at least explain why we are doing what we do below.]
[FP: I tried to play with the epsilon to see if we could get rid of the infinite values in the normalized values. With default epsilon, we have about 40 infinite values, with epsilon 10000, we have about 20. When K = 0, there is no infinite values but the normalized values don't capture as much of biology (looking at the pca with published clusters colors). It seems to me that we get infinite norm. values when the number of parameters to estimate is large. I tried to reduce K to 25 (no infinite but W not as good), 40 (infinite values but W looks ok)... to be continued.]

>>>>

[DR: Fanny, did you figure out why we get infinite values? If not, we need to at least explain why we are doing what we do below.]
[FP: I created a pull request on github. Let me know what you think.]
